---
title: "Chapter 1 "
output: html_notebook
---

# tidytext definition 

We thus define the tidy text format as being a table with one-token-per-row. A token is a meaningful unit of text, such as a word, that we are interested in using for analysis, and tokenization is the process of splitting text into tokens.

## Basic example

```{r}
(text <- c("Because I could not stop for Death -",
          "He kindly stopped for me -",
          "The Carriage held but just Ourselves -",
          "and Immortality"))
```

First step: put it into a tibble. 

```{r}
library(dplyr)
(text_df <- data_frame(line = 1:4, text = text))
```

Not yet tidy; each row has more than one token.

```{r}
library(tidytext)
text_df %>%
  unnest_tokens(output = word, input = text, 
                token = "words") # first argument: name of column where to put tokens.
                            # second argument: name of column where the text lives. 
```
Now, it is tidy!. 

## Jane Austen Example

```{r}
library(janeaustenr)
library(dplyr)
library(stringr)

original_books <- austen_books() %>%
  group_by(book) %>%
  mutate(linenumber = row_number(),
         chapter = cumsum(str_detect(text, regex("^chapter [\\divxlc]",
                                                 ignore_case = TRUE)))) %>%
  ungroup()

original_books
```

Now, as tidy:

```{r}
tidy_books <- original_books %>%
  unnest_tokens(word, text)
tidy_books
```

We can remove stopwords:

```{r}
library(hrbrthemes)
library(ggplot2)
tidy_books %>% anti_join(stop_words) %>%  # stop_words, provided by tidytext package. 
  count(word, sort= TRUE) %>% 
  filter(n > 600) %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(word, n)) +
  geom_col() +
  xlab(NULL) +
  coord_flip() + 
  labs(title = "Most common words used by Jane Austen") +
  theme_ipsum_rc()
```

## Another example 

```{r}
library(gutenbergr)

hgwells <- gutenberg_download(c(35, 36, 5230, 159))

tidy_hgwells <- hgwells %>%
  unnest_tokens(word, text) %>%
  anti_join(stop_words)

tidy_hgwells %>%
  count(word, sort = TRUE)

```

### Final example

 Let’s get Jane Eyre, Wuthering Heights, The Tenant of Wildfell Hall, Villette, and Agnes Grey.
 
```{r}
bronte <- gutenberg_download(c(1260, 768, 969, 9182, 767))

tidy_bronte <- bronte %>%
  unnest_tokens(word, text) %>%
  anti_join(stop_words)

tidy_bronte %>%
  count(word, sort = TRUE)
```
 
```{r}
library(tidyr)
frequency <- bind_rows(mutate(tidy_bronte, author = "Brontë Sisters"),
                       mutate(tidy_hgwells, author = "H.G. Wells"), 
                       mutate(tidy_books, author = "Jane Austen")) %>% 
  mutate(word = str_extract(word, "[a-z']+")) %>%
  count(author, word) %>%
  group_by(author) %>%
  mutate(proportion = n / sum(n)) %>% 
  select(-n) %>% 
  spread(author, proportion) %>% 
  gather(author, proportion, `Brontë Sisters`:`H.G. Wells`)
frequency
```

```{r}
library(scales)

# expect a warning about rows with missing values being removed
ggplot(frequency, aes(x = proportion, y = `Jane Austen`, color = abs(`Jane Austen` - proportion))) +
  geom_abline(color = "gray40", lty = 2) +
  geom_jitter(alpha = 0.1, size = 2.5, width = 0.3, height = 0.3) +
  geom_text(aes(label = word), check_overlap = TRUE, vjust = 1.5) +
  scale_x_log10(labels = percent_format()) +
  scale_y_log10(labels = percent_format()) +
  scale_color_gradient(limits = c(0, 0.001), low = "darkslategray4", high = "gray75") +
  facet_wrap(~author, ncol = 2) +
  theme(legend.position="none") +
  labs(y = "Jane Austen", x = NULL) +
  theme_ipsum_rc()
```

